\chapter*{Acknowledgements}
I would, first of all, extend my gratitude to Dr. Nicolas Gayton and Dr. Alexander Forrester for accepting to review this thesis and Dr. Nathalie Bartoli and Dr. Rodolphe Le Riche for agreeing to be part of the jury. 

The current research work being a CIFRE gave me the fortune to work in both an academic environment (ISAE Toulouse) and a company (Airbus Operations S.A.S.). On the academic side, I would like to thank my tutors Dr. Joseph Morlier and  Dr. Emmanuel Rachelson. They both patiently listened to my wacky ideas and nudged me into more productive directions. They have the capability to understand and explain concepts from their lowest principles, a quality which I admire and would like to replicate.  

At Airbus, I am really indebted to my industrial supervisor Michele Colombo, who took part in developing the wacky ideas and attempting to make them work, working with him has been the exact opposite of a stereotypical Ph.D. I would also like to thank Sebastien Blanc for being encouraging and helping me integrate into the French-speaking environment. He believed in my capabilities and let me apply algorithms in the intensive flight-test campaign. 

I thank the whole EGLRM team at Airbus, my colleagues during the plateau, members of the V\&V IPT, and students at the ICA lab. I have really enjoyed my conversations with Hitul Dhoru, Simon Trapier, Alex Calder, Elisa Bosco and Sebastian Delord. 

As always, I am forever grateful to my family for their love and understanding, my father for his inspiration, my mother for unconditional love, my brother for being my bro and my wife for tolerating my sense of humor. 

While all the above people have shaped me by their presence in the last 3 years, I have learned a lot virtually from the blogs of Vitalik Buterin, tweets of Naval Ravikant and books of Yuval Noah Harari. 

Last but not the least, I in indebted to the ANRT and Airbus Operations S.A.S for funding the research work. 
